---
title: "Cabbages"
author: "Tito Lopez"
date: "Fall 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
library(ggplot2)
library(dplyr)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

$H_0$: There is no difference in the vitamin c content of cabbages based on cultivation method

$H_0$: There is a difference in the vitamin c content of cabbages based on cultivation method

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

Vitamin c content is a numerical variable, cultivation is a factor

```{r}
data = veggy
```

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
ggplot(data, aes(x = Cult, y = VitC)) + geom_boxplot() +
labs(title = "boxplot of VitC by Cult", x = "Cult" , y = "VitC")
```

The difference between c39 and c52 is, c52 averages more production of VitC than c39.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
summary_stats <- data %>%
  group_by (Cult) %>%
  summarise(
  Mean = mean(VitC),
  Median = median(VitC),
  SD = sd(VitC)
)

summary_stats
```

The pattern for c39 is that the mean and median are only 0.5 off from each other. The pattern for c52 is that the mean and median are 0.1 off from each other. Which means all the averages for each cult "c39 and c52" are around the same.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
anova_result <- aov(VitC ~ Cult, data = data)
summary(anova_result)
```

Is a difference on the vitamin c content based cultivation. There is a difference between vitamin c content based on cultivation. I will reject the null hypothesis because it is small.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

